Uncovering Distributed System Bugs\\ during Testing (not Production!)

### 2015-08-21 methodology.tex
update
removed mentions of unmodified as this is wrong

In order to solve this problem, and allow \psharp to be used for testing \emph{unmodified} legacy distributed systems, we decided to take a radically different modeling approach. We provide the capability to model the environment of a system using \psharp, and then allow the developer to take advantage of existing language features, such as \emph{method dispatch}, to connect the system under test with the environmental model, and finally test it using the \psharp systematic concurrency testing engine.

@@

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{img/mocked_engine}
\caption{The model machines that replace the real environment during testing of the Extent Manager.}
\label{fig:azurestoremodel}
\end{figure}

>>>>

In order to solve this problem, and allow \psharp to be used for testing legacy distributed systems, we decided to take a radically different modeling approach. We provide the capability to model the environment of a system using \psharp, and then allow the developer to take advantage of existing language features, such as \emph{method dispatch}, to connect the system under test with the environmental model, and finally test it using the \psharp systematic concurrency testing engine.

@@

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{img/mocked_engine}
\caption{The real environment of the Extent Manager is replaced with a mocked version for testing.}
\label{fig:azurestoremodel}
\end{figure}
